Competing Bandits: \\ The Perils of Exploration under Competition

### 2018-11-06 paper/content/model.tex
Minor edit in the model.

The simulations are computationally intensive. An experiment on a particular MAB instance comprised multiple runs of the competition game: $N$ mean reward vectors times $9$ pairs of algorithms times three values for the warm start. We used a parallel implementation over a cluster of 12 2.2 GHz CPU cores, with 8 GB RAM per core. With this implementation, each experiment took about $10$ hours.

While we experiments with various MAB instances and parameter settings, in the main paper we only report plots for selected, representative experiments. Additional plots can be found in the supplement. Unless noted otherwise, our findings are based on and consistent with all these plots.

>>>>

The simulations are computationally intensive. An experiment on a particular MAB instance comprised multiple runs of the competition game: $N$ mean reward vectors times $9$ pairs of algorithms times three values for the warm start. We used a parallel implementation over a cluster of 12 2.2 GHz CPU cores, with 8 GB RAM per core. Each experiment took about $10$ hours.

\xhdr{Consistency.}
While we experiments with various MAB instances and parameter settings, in the main paper we only report plots for selected, representative experiments. Additional plots can be found in the supplement. Unless noted otherwise, our findings are based on and consistent with all these plots.
